Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Move a sentence in the methods
Add missing ~ before reference to equation

Consider a tesseroid in a geocentric spherical coordinate system defined by
pairs of geocentric latitudinal ($\phi_1$, $\phi_2$), longitudinal ($\lambda_1$,
$\lambda_2$), and radial ($r_1$, $r_2$) boundaries.
We define an external computation point $P(r, \phi, \lambda)$ located at radius $r$,
geocentric latitude $\phi$, and longitude $\lambda$.
The derivatives of the gravitational potential are taken with
respect to the local north-oriented Cartesian coordinate system with origin at $P$
(Fig.~\ref{fig:tesseroid}).
\citet{Grombein2013} provide efficient formulations for the volume integrals of the
gravitational potential and its first- and second-order derivatives of a tesseroid with
homogeneous density.
Here, we will assume that the tesseroid has a density varying with $r$ according to an
arbitrary continuous function $\rho(r)$.
Thus, the integrals for the gravitational potential and its first-order derivatives are
slightly modified to

@@

\noindent
has an analytical solutions for the gravitational potential and its vertical derivative
given by Eqs.~\ref{eq:shell-pot-linear} and \ref{eq:shell-gz}.
The values of the angular and linear coefficients ($a$ and $b$)
can be chosen so that the density assumes the values of $\rho_\text{in} = 3300$~kg/m$^3$
and $\rho_\text{out} = 2670$~kg/m$^3$ on the inner ($R_\text{in}$) and outer
($R_\text{out}$) radii of the shell, respectively,

>>>>

Consider a tesseroid in a geocentric spherical coordinate system defined by
pairs of geocentric latitudinal ($\phi_1$, $\phi_2$), longitudinal ($\lambda_1$,
$\lambda_2$), and radial ($r_1$, $r_2$) boundaries.
We define an external computation point $P(r, \phi, \lambda)$ located at radius $r$,
geocentric latitude $\phi$, and longitude $\lambda$.
\citet{Grombein2013} provide efficient formulations for the volume integrals of the
gravitational potential and its first- and second-order derivatives of a tesseroid with
homogeneous density.
The derivatives of the gravitational potential are taken with
respect to the local north-oriented Cartesian coordinate system with origin at $P$
(Fig.~\ref{fig:tesseroid}).
Here, we will assume that the tesseroid has a density varying with $r$ according to an
arbitrary continuous function $\rho(r)$.
Thus, the integrals for the gravitational potential and its first-order derivatives are
slightly modified to

@@

\noindent
has an analytical solutions for the gravitational potential and its vertical derivative
given by Eqs.~\ref{eq:shell-pot-linear} and~\ref{eq:shell-gz}.
The values of the angular and linear coefficients ($a$ and $b$)
can be chosen so that the density assumes the values of $\rho_\text{in} = 3300$~kg/m$^3$
and $\rho_\text{out} = 2670$~kg/m$^3$ on the inner ($R_\text{in}$) and outer
($R_\text{out}$) radii of the shell, respectively,
